Turtlebot SLAM

### 2013-01-19 trunk/Article/Article.tex
Improvements of the introduction section

\section{Introduction}
Nowadays a lot of tasks are performed by mobile robots, for example transportation, search and rescue and automated vacuum cleaning. To efficiently perform these tasks the robot needs a map of its environment. Sometimes the data about the environment is already available and using for example GPS the robot can locate itself, making the solving of the task at hand easier. But for other tasks the robot should only rely on internal sensors and make its own map of the environment.

The acquisition of these maps has been a major research focus in the robotics community the last decades. Building or learning these maps under the uncertainty of position and the accuracy of measurements is often referred to as the Simultaneous Localization And Mapping (SLAM) problem. A large variety of solutions is available to the SLAM problem, these approaches can be classified as either filtering or smoothing.

Filtering approaches model the problem as an on-line state estimation where the state of the system consists in the current robot position and the map. New measurements augment and refine the estimate as they come available. Due to their incremental nature these filtering approaches are usually referred to as on-line SLAM methods. The other type of approach estimates the full trajectory from the full set of measurements. These approaches address the so called full SLAM problem and they typically rely on least-square error minimization techniques.

@@

The rest of this paper is structured as follow. Section 2 will provide the reader with the necessary background information on this topic.

@@

\subsection{Problem Statement}
The focus of this paper is SLAM, more specifically GraphSLAM and how it is used to construct a map of an unknown environment. GraphSLAM returns as a result the optimal graph representing the path the robot has explored. There is also the need for exploration to map the still unseen areas of the space where the robot is located. Since the goal of the robot in this paper is to map the entire area where it has been placed. The data returned by the GraphSLAM algorithm is turned into a occupancy grid map and then used for the autonomous exploration. Each time the robot takes another sensor measurement of its surroundings a node is added to the data in the GraphSLAM algorithm, all the obstacles detected in a measurement are as reference points to optimize the graph. The algorithm is tested in a robot simulator named STAGE with a provided map.

>>>>

\section{Introduction}
Nowadays a lot of tasks are performed by mobile robots, for example transportation, search and rescue and automated vacuum cleaning (figure \ref{fig:vacuum_cleaner}). To efficiently perform these tasks the robot needs a map of its environment. Sometimes the data about the environment is already available as a map. Using for example GPS the robot can then locate itself, making the planning and solving of the task at hand easier. But for tasks in unknown environments or where external referencing  like GPS is unavailable the robot should only rely on internal sensors and make its own map of the environment.

The acquisition of these maps has been a major research focus in the robotics community the last decades \cite{Grisetti}. Building or learning these maps under position uncertainty with inaccurate sensor measurements is often referred to as the Simultaneous Localization And Mapping (SLAM) problem. A large variety of solutions is available to the SLAM problem, these approaches can be classified as either filtering or smoothing.

Filtering approaches model the problem as an on-line state estimation. The state of the system consists in the current robot position and the map. New measurements augment and refine the estimate as they become available. Due to their incremental nature these filtering approaches are usually referred to as on-line SLAM methods. The other type of approach estimates the full trajectory from the full set of measurements. These approaches address the so called full SLAM problem and they typically rely on least-square error minimization techniques.

@@

The rest of this paper is structured as follows. Section 2 will provide the reader with the necessary background information on this topic. Section 3 is about the implementation details of the methods used. Section 4 will explain the experiments ran to validate and benchmark the implemented methods and also evaluate the obtained results. Section 5 discusses the acquired results of the experiments and proposes further research based on those. And the last section wraps up the paper with the conclusions of this research.

@@

\subsection{Problem Statement}
The focus of this paper is SLAM, more specifically GraphSLAM and how it is used to construct a map of an unknown environment. GraphSLAM returns as a result the optimized graph representing the path the robot has explored. Because the goal of the robot in this paper is to map the entire area where it has been placed. There is also the need for an exploration strategy to map the still unseen areas of the space where the robot is located. The results returned by the GraphSLAM algorithm are turned into an occupancy grid map and then used for the autonomous exploration. The algorithm is tested in a robot simulator called STAGE which simulates a provided map.
